partial: An R Package for Creating Partial Dependence Plots

### 2016-09-01 manuscript/greenwell.tex
note to add something
updated abstract
added xgboost to supported models tabel

\abstract{
Complex nonparametric models---like neural networks, random forests, and support vector machines---are more common than ever in predictive analytics, especially when dealing with large observational databases that don't adhere to the strict assumptions imposed by traditional statistical techniques (e.g. multiple linear regression). Unfortunately, it can be challenging for the uninitiated to understand the results of such models and explain them to management. Partial dependence plots offer a simple solution. Partial dependence plots are low-dimensional graphical renderings of the prediction function $\widehat{f}\left(\boldsymbol{x}\right)$ so that the relationship between the outcome and predictors of interest can be easily understood. These plots are especially useful in explaining the output from complex black box models like support vector machines or neural networks or constructing simpler parsimonious models on newly obtained data.
}

@@

@@

Currently supported models are described in Table~\ref{tab:models}. While more models will be added as the package grows, the \code{partial.default} method should be able to handle many others not listed in Table~\ref{tab:models}; for example, neural networks from the \CRANpkg{nnet} package \citep{venables-modern-2002} and projection pursuit regression \citep{friedman-ppr-1981} using the \code{ppr} function in the \pkg{stats} package.
\begin{table}[htbp]
  \begin{tabular}{p{4cm}ll}
    \toprule
      Type of model & R package & Object class \\
      \midrule
      Decision tree             & \CRANpkg{rpart} \citep{rpart-pkg} & \code{"rpart"} \\
                                & \pkg{party}    & \code{"BinaryTree"} \\
                                & \pkg{partykit} & \code{"constparty"}/\code{"party"} \\
      Bagged decision trees     & \CRANpkg{ipred} \citep{ipred-pkg} & \code{"classbagg"}, \code{"regbagg"} \\
                                & \CRANpkg{adabag} \citep{adabag-pkg} & \code{"bagging"} \\
      Boosted decision trees    & \pkg{gbm}      & \code{"gbm"} \\
                                & \CRANpkg{adabag} \citep{adabag-pkg} & \code{"boosting"} \\
      Random forest & \pkg{randomForest} & \code{"randomForest"} \\
      Conditional random forest & \pkg{party}    & \code{"RandomForest"} \\
                                & \pkg{partykit} & \code{"cforest"} \\
      Linear model              & \pkg{stats}    & \code{"lm"} \\
      Generalized linear model  & \pkg{stats}    & \code{"glm"}, \code{"lm"} \\
      Multivariate adaptive regression splines (MARS) & \CRANpkg{earth} \citep{earth-pkg} & \code{"earth"} \\
      Support vector machine    & \CRANpkg{e1071} \citep{e1071-pkg} & \code{"svm"} \\
                                & \CRANpkg{kernlab} \citep{kernlab-pkg} & \code{"ksvm"} \\
      \bottomrule
  \end{tabular}
  \caption{Models specifically supported by the \pkg{package}.}
  \label{tab:models}
\end{table}

>>>>

\abstract{
Complex nonparametric models---like neural networks, random forests, and support vector machines---are more common than ever in predictive analytics, especially when dealing with large observational databases that don't adhere to the strict assumptions imposed by traditional statistical techniques (e.g. multiple linear regression). Unfortunately, it can be challenging for the uninitiated to understand the results of such models and explain them to management. Partial dependence plots offer a simple solution. Partial dependence plots are low-dimensional graphical renderings of the prediction function $\widehat{f}\left(\boldsymbol{x}\right)$ so that the relationship between the outcome and predictors of interest can be easily understood. These plots are especially useful in explaining the output from complex black box models like support vector machines or neural networks or constructing simpler parsimonious models on newly obtained data. In this paper, we introduce partial, a general R package for creating partial dependence plots.
}

@@

\strong{Mention the integral approximation!!}

@@

Currently supported models are described in Table~\ref{tab:models}. While more models will be added as the package grows, the \code{partial.default} method should be able to handle many others not listed in Table~\ref{tab:models}; for example, neural networks from the \CRANpkg{nnet} package \citep{venables-modern-2002} and projection pursuit regression \citep{friedman-ppr-1981} using the \code{ppr} function in the \pkg{stats} package.
\begin{table}[htbp]
  \begin{tabular}{p{4cm}ll}
    \toprule
      Type of model & R package & Object class \\
      \midrule
      Decision tree             & \CRANpkg{rpart} \citep{rpart-pkg} & \code{"rpart"} \\
                                & \pkg{party}    & \code{"BinaryTree"} \\
                                & \pkg{partykit} & \code{"constparty"}/\code{"party"} \\
      Bagged decision trees     & \CRANpkg{ipred} \citep{ipred-pkg} & \code{"classbagg"}, \code{"regbagg"} \\
                                & \CRANpkg{adabag} \citep{adabag-pkg} & \code{"bagging"} \\
      Boosted decision trees    & \pkg{gbm}      & \code{"gbm"} \\
                                & \CRANpkg{xgboost} \citep{xgboost-pkg} & \code{"xgb.Booster"}
                                & \CRANpkg{adabag} \citep{adabag-pkg} & \code{"boosting"} \\
      Random forest & \pkg{randomForest} & \code{"randomForest"} \\
      Conditional random forest & \pkg{party}    & \code{"RandomForest"} \\
                                & \pkg{partykit} & \code{"cforest"} \\
      Linear model              & \pkg{stats}    & \code{"lm"} \\
      Generalized linear model  & \pkg{stats}    & \code{"glm"}, \code{"lm"} \\
      Multivariate adaptive regression splines (MARS) & \CRANpkg{earth} \citep{earth-pkg} & \code{"earth"} \\
      Support vector machine    & \CRANpkg{e1071} \citep{e1071-pkg} & \code{"svm"} \\
                                & \CRANpkg{kernlab} \citep{kernlab-pkg} & \code{"ksvm"} \\
      \bottomrule
  \end{tabular}
  \caption{Models specifically supported by the \pkg{package}.}
  \label{tab:models}
\end{table}
